\sc Cells at War: The Playfulness of Game-Based Learning

### 2023-04-02 thesis_template/paper0904.tex
Results section done, only discussion now

%%%%%Types of courses taken by students
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/types_of_courses_taken.jpg}
	\caption{Types of Courses Taken}
	\label{fig:2}
\end{figure}

Students were asked to reflect on their experiences as undergraduate students at McMaster University. Participants responded to two questions regarding how much coursework has emphasized certain aspects of their learning \figref{fig:3}, and how often they have applied their learning in different contexts \figref{fig:4}. 62

%%%%%During the current school year how much has your coursework emphasized the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/howmuch_coursework_emphasized_thefollowing.jpg}
	\caption{How Much Has Coursework Emphasized the following}
	\label{fig:3}
\end{figure}

%%%%%During the current school year how often would you say you have done the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_often_haveyou_done_thefollowing.jpg}
	\caption{How often have you done the following}
	\label{fig:4}
\end{figure}

@@

%%%%%If game-based learning approaches were incorporated into one of your science courses, how do you think that this mode of learning can help with the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_does_gbl_help_in_science.jpg}
	\caption{If game-based learning approaches were incorporated in your science courses}
	\label{fig:5}
\end{figure}

%%%%% If BIO1A03 added a game-based learning component, how much would this improve your motivation to do the following?
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/ifbio1a03_added_gblcomponent.jpg}
	\caption{If BIO1A03 added a game-based component}
	\label{fig:6}
\end{figure}

%%%%% How likely is it that you would play the video game Cells at War on your own time, outside of class to further consolidate material taught during this class
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_likely_you_would_play_cellsatwar.jpg}
	\caption{How likely is it you would play Cells at War outside of class}
	\label{fig:7}
\end{figure}

%%%%%How prepared would you feel if you were given a quiz on Pompe Disease based on the Cells at War game, compared to studying off traditional lecture slides
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_prepared_if_tested_on_pompe_based_off_cellsatwar.jpg}
	\caption{How prepared would you feel if given a quiz on Pompe Disease}
	\label{fig:8}
\end{figure}

>>>>

%%%%%Types of courses taken by students
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/types_of_courses_taken.jpg}
	\caption{Student responses regarding the different types of courses taken at McMaster University in 2022}
	\label{fig:2}
\end{figure}

Students were asked to reflect on their experiences as undergraduate students at McMaster University. Participants responded to two questions regarding how much coursework has emphasized certain aspects of their learning \figref{fig:3}, and how often they have applied their learning in different contexts \figref{fig:4}. The majority of students responded that their coursework emphasized applying facts to new problems, analyzing ideas in depth, and forming new ideas from various pieces of information "quite a bit". In the case of memorizing course material however, 41\% of participants responded this was emphasized "very much" in their courses.

%%%%%During the current school year how much has your coursework emphasized the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/howmuch_coursework_emphasized_thefollowing.jpg}
	\caption{Student responses regarding how much their coursework has emphasized the following aspects}
	\label{fig:3}
\end{figure}

\figref{fig:4} follows a similar format to the previous question. Students were asked how often they had combined ideas from different courses when completing assignments, connected their learning to societal issues, learned something that changed understanding of an issue and connected ideas from courses to prior experiences and knowledge. Most students responded doing these things "sometimes" or "often", with a smaller number of participants responding "very often". It is worthwhile to note that 43\% of students indicated that they "sometimes" connect what they have learned to societal or health related issues. As science students, it is important to connect what has been learned to societal and health related issues, as the concepts we study are interwoven throughout all facets of life. Implementing game based learning into science classrooms has the potential to change this narrative by presenting concepts to students in the form of real world examples, rather than static textbook diagrams.

%%%%%During the current school year how often would you say you have done the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_often_haveyou_done_thefollowing.jpg}
	\caption{Student responses regarding how often they have done the following things during the school year}
	\label{fig:4}
\end{figure}

@@

After the questions regarding current undergraduate experiences, students were asked to reflect on their feelings towards implementing game-based learning approaches into their classrooms.

Following the same question structure as \figref{fig:4}, students were asked how implementing game-based learning into any one of their science courses could help in a wide variety of areas. Interestingly, across all four areas, we see an increase in the number of students who responded "very much", compared to the number of students who responded "very much" in \figref{fig:4}. Through implementing game based learning methods in science classrooms, more students would feel better suited to combine ideas from different courses when completing assignments, connect their learning to societal and health related issues and connect ideas from courses to prior experiences and knowledge. Following the same question structure as \figref{fig:3}, \figref{fig:6} shows how motivation to do certain things can be improved in BIO1A03 if a game-based learning component was added. In general, students indicated that a game-based learning component in BIO1A03 would improve motivation to connect ideas to societal issues, learn something that changes understanding and connect ideas from courses to prior experiences and knowledge "very much". In comparison to \figref{fig:3}, there is a clear increase in the number of responses which indicate "very much". The only exception however is in terms of motivation to memorize course material. There was a decrease in the number of students who reported that if BIO1A03 added a game-based learning component, it would motivate them to memorize course material. This is exactly the aim of game-based learning approaches, to emphasize exploration and understanding, not memory.

%%%%%If game-based learning approaches were incorporated into one of your science courses, how do you think that this mode of learning can help with the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_does_gbl_help_in_science.jpg}
	\caption{Student responses regarding how game-based learning approaches could help with the following things if implemented in science courses}
	\label{fig:5}
\end{figure}

%%%%% If BIO1A03 added a game-based learning component, how much would this improve your motivation to do the following?
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/ifbio1a03_added_gblcomponent.jpg}
	\caption{Student responses regarding how motivation to do the following things would improve if BIO1A03 added a game-based learning component}
	\label{fig:6}
\end{figure}

The final two questions provided insight into students' feelings towards not only game-based learning, but specifically towards Cells at War. Students were asked how likely it is that they would play Cells at War outside of class on their own time to further consolidate material taught during class \figref{fig:7}. The results indicated that 43\% of students were somewhat likely to do this, while about 17\% of students reported being very likely to this. 21\% of participants indicated they would not be very likely to do this. These results highlight the potential game-based learning has to be utilized not only as an instructional tool in class, but also as a form of practice and content mastery for students.

%%%%% How likely is it that you would play the video game Cells at War on your own time, outside of class to further consolidate material taught during this class
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_likely_you_would_play_cellsatwar.jpg}
	\caption{Student responses regarding how likely they would be to play Cells at War on their own time, outside of class to further consolidate material taught during class}
	\label{fig:7}
\end{figure}

To assess if students understood the content shown to them in game, they were asked how prepared they would feel if given a quiz on Pompe Disease based off playing Cells at War, compared to studying off traditional lecture slides \figref{fig:8}. 52\% of students indicated they would be somewhat prepared, and 17\% of students indicated they would feel very prepared. This strengthens the argument that again, game-based learning is not only an in-class intervention. Video games promote practice, critical thinking, and content mastery, all of which are important aspects when preparing for assessment. Students are willing to try alternative studying methods, and giving them the ability to study in a way that is engaging and interacting could have positive benefits on performance.

%%%%%How prepared would you feel if you were given a quiz on Pompe Disease based on the Cells at War game, compared to studying off traditional lecture slides
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_prepared_if_tested_on_pompe_based_off_cellsatwar.jpg}
	\caption{Student responses regarding how prepared they would feel if given a quiz on Pompe Disease based off Cells at War compared to studying off traditional lecture slides}
	\label{fig:8}
\end{figure}
